### 2022-05-16 manuscript.Rmd
Update statements

  \noindent We have no conflict of interest to disclose. There were no ethical concerns since we did not collect any new data.
  Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: enge@cbs.mpg.de

@@

The data for this study is available  from an   [Open Science Framework repository](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

The data for this study is available  from an   [Open Science Framework repository](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

# Contributions

@@

>>>>

@@

The datasets generated and analyzed during the current study are available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

The analysis code for the current study is available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

# Author contributions

@@

# Competing interests

\noindent The authors declare no competing interests.

# Corresponding author

\noindent Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: [enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)
